\begin{tabularx}{\textwidth}{Y}
  {\large University of Evansville Lesson Plan Format 8/29/2025} \\
  \arrayrulecolor{blue} \hline \\
\end{tabularx}


\arrayrulecolor{black} 
\begin{tabularx}{\textwidth}{|X|X|}
  \hline 
  \textcolor{blue}{Name:} Randall Helzerman         &   \textcolor{blue}{Student ID Number:} 0128861 \\
  \hline 
  \textcolor{blue}{Course Number:} EDUC-497-03 2025FA &   \textcolor{blue}{Instructor Name:} Dr. Laura Watkins\\
  \hline 
\end{tabularx}
\arrayrulecolor{black}

\vskip 10pt

\begin{tabularx}{\textwidth}{Y}
  {\bf Lesson Overview} \\
\end{tabularx}
\arrayrulecolor{black}


\arrayrulecolor{black} 
\begin{tabularx}{\textwidth}{|X|X|}
  \hline 
  \textbf{Lesson Title:} \\
  
  \hline 
  \textbf{Subject:} Math\\
  
  \hline 
      {
        \begin{tabularx}{\textwidth}{X|X}
          \hskip -6pt
          \textbf{Duration of Lesson: 80 min} & \textbf{Grade Level(s)/Course:} 8th grade\\
        \end{tabularx}
      } \\
      
      \hline
      
      \textbf{Lesson Description: THE PYTHAGOREAN THEOREM} (in all-caps!)\\
      
      \hline
      
      \textbf{Standards and/or Indicator(s):}\\
      \textbf{Indiana Standard number:} 8.GM.8\\
      \textbf{Text:} Apply the Pythagorean Theorem to determine unknown side lengths in right triangles in real-world and other
      mathematical problems in two dimensions.\\
      \hline
      
      \textbf{Learning Objective(s)/Target:} \\
             {\begin{enumerate}
               \item Students should know what a right triangle is
               \item Students should feel comfortable 
             \end{enumerate}} \\
             \hline
             
             \textbf{Lesson Resources/Technology: } 6 3x5 cards for a Pythagorean triple treasure hunt\\
             \hline
             
             \textbf{Key Vocabulary:} 
             Right angle, right triangle, legs of right triangle, hypoteneus of a right triangle. \\
             \hline
\end{tabularx}
\arrayrulecolor{black}

\pagebreak

\begin{tabularx}{\textwidth}{|p{0.5in}|X|}
  \hline
  \centerline{\textbf{\large Time}} &  \textbf{\large Instructional Sequence } \\
  \hline
  \textbf{5 min} &  \textbf{\em Introduction/Anticipatory Set:}     Draw the following figures on the Promethean board: \\
  10 min & 
  \begin{tikzpicture}[scale=0.9]
    
    % Row 1, Column 1 - Problem 1 (3-4-5 triangle)
    \begin{scope}[shift={(0,0)}]
      \draw[thick] (0,0) -- (4,0) -- (0,3) -- cycle;
      \draw (0.3,0) -- (0.3,0.3) -- (0,0.3);
      \node[below] at (2,0) {4};
      \node[left] at (0,1.5) {3};
    \end{scope}
    
    % Row 1, Column 2 - Problem 2 (5-12-13 triangle)
    \begin{scope}[shift={(5,0)}]
      \draw[thick] (0,0) -- (5,0) -- (0,2.4) -- cycle;
      \draw (0.3,0) -- (0.3,0.3) -- (0,0.3);
      \node[below] at (2.5,0) {5};
      \node[above right] at (2.5,1.2) {13};
    \end{scope}
    
    % Row 1, Column 3 - Problem 3 (6-8-10 triangle)
    \begin{scope}[shift={(11,0)}]
      \draw[thick] (0,0) -- (4,0) -- (0,3) -- cycle;
      \draw (0.3,0) -- (0.3,0.3) -- (0,0.3);
      \node[below] at (2,0) {8};
      \node[above right] at (2,1.5) {10};
    \end{scope}
    
    % Row 2, Column 1 - Problem 4 (7-24-25 triangle)
    \begin{scope}[shift={(0,-4)}]
      \draw[thick] (0,0) -- (3.5,0) -- (0,2.4) -- cycle;
      \draw (0.3,0) -- (0.3,0.3) -- (0,0.3);
      \node[below] at (1.75,0) {7};
      \node[above right] at (1.75,1.2) {25};
    \end{scope}
    
    % Row 2, Column 2 - Problem 5 (8-15-17 triangle)
    \begin{scope}[shift={(5,-4)}]
      \draw[thick] (0,0) -- (4,0) -- (0,3) -- cycle;
      \draw (0.3,0) -- (0.3,0.3) -- (0,0.3);
      \node[below] at (2,0) {15};
      \node[left] at (0,1.5) {8};
    \end{scope}
    
    % Row 2, Column 3 - Problem 6 (9-12-15 triangle)
    \begin{scope}[shift={(11,-4)}]
      \draw[thick] (0,0) -- (4,0) -- (0,3) -- cycle;
      \draw (0.3,0) -- (0.3,0.3) -- (0,0.3);
      \node[below] at (2,0) {12};
      \node[left] at (0,1.5) {9};
    \end{scope}
    
  \end{tikzpicture}  \\

  & Ask the students to write on their whiteboards what the labeled
  sides are for each triangle: Is it the hypoteneus, or a leg? \\
  
  \hline
  
  \textbf{} &

  \textbf{\em Demonstrate, Build, Apply Knowledge} We had a Pythagorean triangle treasure hunt.  At 6 stations around the room there was a problem involving a right triangle, and the solution told the students which station to go to next.  If they arrived back at their first station, they won!  See figure \ref{th_pt} for the cards.\\
  
  \hline
  
  \textbf{} & \textbf{\em Depth of Knowledge Questions:} Had students take out their whiteboards, and list out how many kinds of objects they could see in the room which had right angles.  Let them look around for 5 minutes.

  The students were quite surprised by how many there were.   Some students could name over 50 different kinds of objects (blocks the wall was made of, ceiling tiles, posters on the walls, the walls, etc etc).

  I told them I wanted them to do this exercise because the world they happened to find themselves in is just FULL of right angles, and therefore, right triangles.  And that I wanted them to feel comfortable and safe in their world, and in order to do that, they had to be able to understand their world.   And since their world has so many right angles, a good place to start would be learning the Pythagorean theorem.\\
  
  \hline
  
  \textbf{} & \textbf{\em Guided Practice:} Cold-calling the students, asking them how to identify the variios parts of a right triangle, and how to calculate the lengths of the hypoteneuse.\\
  
  \hline
  
  \textbf{} & \textbf{\em Independent Practice:} Work on some problems from workbook  \\
  
  \hline

  \textbf{} & \textbf{\em Assessment:} We gave an exit ticket to test basic knowledge.\\
  \hline
  
  \textbf{} & \textbf{\em Wrap Up/Closing Activity/Reflection:} N/A\\
  
  \hline
\end{tabularx}
  
\vskip 6pt

\begin{small}
\begin{tabularx}{\linewidth}{|p{2.1in}|X|}
  \hline
  \textbf{Differentiation/Accommodations and/or Modifications: } & Paid more attention to explaining what ``consecutive numbers'' meant.   Most students were not familiar with the word ``consecutive.''\\
  \hline
  \textbf{Culturally Responsive Teaching/ Diversity and Inclusion: } & N/A\\
  \hline
\end{tabularx}

\vskip 6pt

\begin{tabularx}{\linewidth}{|X|}
  \hline
  \textbf{Self-Reflection:} \\
  \textbf{My Teaching:} 
  \begin{enumerate}
  \item After looking at the exit tickets from the first session, it was obvious that I had not done enough explaining what ``consecutive numbers'' were.   I modified my approach and the next session did much better on the exit ticket.
  \item .
  \end{enumerate} \\
  
  \textbf{The Students:}
  \begin{enumerate}
  \item The students really liked the treasure hunt, and they really liked naming out all of the things in the room which had right angles.  
  \item They were amazed that there were so many.  
  \end{enumerate} \\
  
  \textbf{The Lesson:}
  \begin{enumerate}
  \item As noted above, the lesson was a bit thin on explaining what ``consecutive numbers'' were.  
  \end{enumerate} \\
  
  \hline
\end{tabularx}
\end{small}
