\begin{tabularx}{\textwidth}{Y}
  {\large University of Evansville Lesson Plan Format } \\
  \arrayrulecolor{blue} \hline \\
\end{tabularx}


\arrayrulecolor{black} 
\begin{tabularx}{\textwidth}{|X|X|}
  \hline 
  \textcolor{blue}{Name:} Randall Helzerman         &   \textcolor{blue}{Student ID Number:} 0128861 \\
  \hline 
  \textcolor{blue}{Course Number:} EDUC-497-03 2025FA &   \textcolor{blue}{Instructor Name:} Dr. Laura Watkins\\
  \hline 
\end{tabularx}
\arrayrulecolor{black} 

\vskip 10pt
  
\begin{tabularx}{\textwidth}{Y}
  {\bf Lesson Overview} \\
\end{tabularx}
\arrayrulecolor{black}


\arrayrulecolor{black} 
\begin{tabularx}{\textwidth}{|X|X|}
  \hline 
  \textbf{Lesson Title:} \\
  
  \hline 
  \textbf{Subject:} Math\\
  
  \hline 
      {
        \begin{tabularx}{\textwidth}{X|X}
          \hskip -6pt
          \textbf{Duration of Lesson:} & \textbf{Grade Level(s)/Course:} 8th grade\\
        \end{tabularx}
      } \\
      
      \hline
      
      \textbf{Lesson Description: {\tiny (Describe the primary nature e.g. hands-on, direct instruction, inquiry, project based etc. of the lesson)}} \\
        
        \hline
        
        \textbf{Standards and/or Indicator(s):} {\tiny Cut and paste from IDOE website here. Feel free to replicate the descriptors listed below to include more standards in this section.} \\
        \textbf{Indiana Standard number:} \\
        \textbf{Text:} \\
        \hline
        
        \textbf{Learning Objective(s)/Target:} {\tiny What do I want students to learn and be able to do at the end of the lesson? (I can statements)}
               {\begin{enumerate}
                 \item I can multiply two positive numbers, a positive
                   and a negative number, and two negative numbers.
                 \item I can tell how many solutions a square root problem has.
                 \item I can tell how many solutions a cube root problem has.
               \end{enumerate}} \\
               \hline
               
               \textbf{Lesson Resources/Technology: } Each desk has a small whiteboard and a marker which the kids can work problems out on.\\
               \hline
               
               \textbf{Key Vocabulary:} 
                      {\begin{enumerate}
                        \item Square of a number
                        \item Cube of a number
                        \item Square root of a number
                        \item Cube root of a number
                        \item Square is the inverse of Square root
                        \item Cube is the inverse of a Qube root
                      \end{enumerate}} \\
                      \hline
\end{tabularx}
\arrayrulecolor{black}

\pagebreak

\begin{tabularx}{\textwidth}{|p{0.5in}|X|}
  \hline
  \centerline{\textbf{\large Time} 80min} &  \textbf{\large Instructional Sequence } \\
  \hline
  
  \textbf{} & \textbf{\em Introduction/Anticipatory Set:} Put 6
  problems on the promethean board.  These are simple mutiplication
  problems multiplying various combinations of positive and negative
  numbers together.

  The students are not asked to find the numeric value of the answer,
  but merely whether or not the numbers are positive or negative.
  
  They individually write the answers on their small whiteboards.
  Then we have them check their answers with a partner.  Finally, we
  review the correct answers as a class. \\
  
  \hline
  \textbf{} &  \textbf{\em Demonstrate, Build, Apply Knowledge}   \\
  \hline
  \textbf{} &  \textbf{\em Depth of Knowledge Questions:} Students work lecture notes written in their workbooks.\\
  \hline
  \textbf{} &  \textbf{\em Guided Practice:} As per Mrs. Toelle's suggestion, pulled two students (including student D described above) into a small group for more focused tutalage.  This provided an environment which allowed the students to focus more on learning and doing the assignment (a somewhat euphemistic description).   To very good effect: both students were able to independently solve the problems after about 20 minutes of tutalage.  \\
  \hline
  \textbf{} &  \textbf{\em Independent Practice:} Students work on exercise given in the notebook. \\
  \hline
  \textbf{} &  \textbf{\em Assessment:} Exercises reviewed at end of class. \\
  \hline
  \textbf{} &  \textbf{\em Wrap Up/Closing Activity/Reflection:} N/A  \\
  \hline
\end{tabularx}

\vskip 6pt

\begin{small}
\begin{tabularx}{\linewidth}{|p{2.1in}|X|}
  \hline
  \textbf{Differentiation/Accommodations and/or Modifications: } & Wnfortunagely.  Still need to find a way to address the students who are zooming ahead of the rest of the class.  However, the small group was very helpful for participants, including  student D.\\
  \hline
  \textbf{Culturally Responsive Teaching/ Diversity and Inclusion: } & None \\ 
  \hline
\end{tabularx}

\vskip 6pt

\begin{tabularx}{\linewidth}{|X|}
  \hline
  \textbf{Self-Reflection:} \\
  \textbf{My Teaching:} 
  \begin{enumerate}
  \item I was very happy how the small group study went.
  \end{enumerate} \\
  
  \textbf{The Students:}
  \begin{enumerate}
  \item Student D would absolutely thrive with more individualized instruction.  Alas, there is a limited amount of time we have for this, but we will do what we can.
  \end{enumerate} \\
  
  \textbf{The Lesson:}
  \begin{enumerate}
  \item Nothing particularly salient stands out to be said.
  \end{enumerate} \\
  
  \hline
\end{tabularx}
\end{small}
